DisCon Kids Pilot

### 2019-01-16 analysis/02_kids_600.Rmd
new analysis file for kids data

log <- read_excel("../../DisCon-subject_log.xlsx", 1)%>%
  filter(Condition == "d600")%>%
  mutate(dob = as.Date(dob))%>%
  select(subid,experimenter,keep_drop,sex,dob)

#unique(log$subid)
#sum(log$keep_drop == "drop")

@@

unique(data$subid)

@@

```{r sanity checks}
data %>%
  filter(phase == 'training') %>%
  group_by(subid) %>%
  summarise(correct = mean(correct_item))

@@

data %>%
  filter(!subid %in% drop) %>%
  group_by(subage) %>%
  summarise(n = length(unique(subid)))

```
# Proportion correct choice in training trials

>>>>

#unique(raw_data$subid)

# linking the data to the demographics spreadsheet
# always check if subjects get "lost" due do differetn subids
log <- read_excel("../../DisCon-subject_log.xlsx", 1)%>%
  filter(Condition == "d600")%>%
  mutate(dob = as.Date(dob))%>%
  select(subid,experimenter,keep_drop,sex,dob)

#unique(log$subid)

@@

#unique(data$subid)

@@

```{r sanity checks}
# filtering out subjects that perform poorly on training trials
data %>%
  filter(phase == 'training') %>%
  group_by(subid) %>%
  summarise(correct = mean(correct_item))

@@

data <- data %>%
  filter(!subid %in% drop)
```

# Participants

```{r}
data %>%
  group_by(subage)%>%
  summarise(n = length(unique(subid)))%>%
  knitr::kable(digits = 2)
```

# Proportion correct choice in training trials
